# Tables

The easiest way to create a table is to use Excel to input the information for your table and save it as a CSV file.
Then you can read in the CSV file, and use the `kable()` function from **knitr** to style the table.

````
```{r nice-tab}
#Read in data
gopher = readr::read_csv('../data/tab-gopher-women-sports.csv')

# Create table
knitr::kable(
  gopher, 
  caption = "2017 Ticket Sales and Operating Revenue for the University of Minnesota Women's Athletic Teams",
  booktabs = TRUE
)
```
````

Further table styling can be carried out via the **kableExtra** package; see [here](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf).
Below we demonstrate some of that functionality.

````
```{r nice-tab-2}
library(kableExtra)

knitr::kable(
  gopher, 
  caption = "2017 Ticket Sales and Operating Revenue for the University of Minnesota Women's Athletic Teams",
  booktabs = TRUE,
  format = "latex"
  ) %>%
  footnote(general = "Data obtained from the 2017 NCAA Financial Report")
```
````

You can also create the table from within R itself and then use `kable()`.

````
```{r}
flights = readr::read_csv('../data/flights.csv')
tab = flights %>%
  filter(month == 12, day == 24) %>%
  group_by(carrier_name) %>%
  summarize(
    Departure = mean(dep_delay),
    Arrival = mean(arr_delay)
    ) %>%
  select(Carrier = carrier_name, Departure, Arrival)

knitr::kable(
  tab, 
  caption = "Average Departure and Arrival Delay (in Minutes) by Carrier on Decemebr 24",
  booktabs = TRUE,
  format = "latex",
  digits = 2
  )
```
````

Finally, you can also reference tables generated from `knitr::kable()`, e.g., see Table `\@ref(tab:nice-tab)`.